---
title: "论贸易战对中国未来经济的影响"
author: "yimeng"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
# 文档类型:
# 本科: document-bachelor: true
# 专硕: document-premaster: true
# 硕士: document-master: true
# 博士: document-doctor: true
document-bachelor: true
abstract-zh: "中文摘要: RUCThesis 是根据中国人民大学《本科论文指导手册》和《研究生学位论文及其摘要的撰写和印制要求》而制作的 \\LaTeX\\ 论文模板。"
abstract-en: "This is a English abstract."
baseinfo:
  subtitle: "基于统计模拟的经济学预测方法"
  studentid: "20163160102"
  school: "统计学院"
  field: "经济统计学"
  advisor: "yalei"
  grade: ""
  thesiscode: "论文编码：RUC-BK-专业代码-学号 RUC-BK-050101-2014201237"
  score: "4.0"
  date: "`r Sys.Date()`"
  keywordzh: ["贸易战", "经济"]
  keyworden: ["Trade War", "Economics"]
masterinfo:  # 研究生，设置英文标题和主题词, 本科生不需要填写
  etitle: "LaTeX template of Renmin university of China"
  keywords: "Keywords 论文主题词"
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# bookdown介绍

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

每一个Rmd文件只包含一章内容，每一章由一个一级标题`#`来指定。

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

你需要安装XeLaTeX来将这个示例编译为PDF，推荐你去 [这个网站](https://yihui.name/tinytex/) 安装TinyTex，它是包含XeLaTex的。

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
